Web-based Supplementary Materials for Combinatorial Mixture Models for Single-Cell Assays with Application to Vaccine Studies by Greg Finak, Steve De Rosa, Mario Roederer and Raphael Gottardo

### 2012-07-31 WebSupplementaryMaterialMIMOSA.tex
Minor changes. Added "this figure appears in color …" to each figure caption as required.
Signed-off-by: Greg Finak <gfinak@fhcrc.org>

  %  \node at (8,-4) [font=\small\sffamily] {F} ;
%    \node at (0,-7.75) [font=\small\sffamily] {G} ;
  %  \node at (8,-7.75) [font=\small\sffamily] {H} ;
   % \node at (0,-11.75) [font=\small\sffamily] {I} ;
   % \node at (8,-11.75) [font=\small\sffamily] {J} ;
    \end{tikzpicture}
   \caption{Comparison of MIMOSA on other cytokines and cytokine combinations for ENV-1-PTEG stimulated CD4+ T-cells from the HVTN065 trial.}
\label{webfig:HVTN065Results}
\end{figure}

@@

\begin{figure} %  figure placement: here, top, bottom, or page
   \centering
\begin{tikzpicture} [auto,node distance=0cm]
%\node at (0,0) (A) {
%\begin{tikzpicture}
%    \node[anchor=south west,inner sep=0] at (0,0) (a) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_ROC_5000.pdf}};
%    \begin{scope} [x={(a.south east)},y={(a.north west)}]
%        \node at (0,1) [font=\small\sffamily] {A} ;
%    \end{scope}
%    \end{tikzpicture}
%    };
%    \node [right=of A] (B) {
%    \begin{tikzpicture}
%    \node[anchor=south west, inner sep=0] at (0,0) (b) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_FDR_5000.pdf}};
%        \begin{scope} [x={(b.south east)},y={(b.north west)}]
%        \node at (0,1) [font=\small\sffamily] {B} ;
%        \end{scope}
%    \end{tikzpicture}
%    };
    \node at (0,0) (A) {
    \begin{tikzpicture}
     \node[anchor=south west,inner sep=0] at (0,0) (c) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_ROC_5000.pdf}};
         \begin{scope} [x={(c.south east)},y={(c.north west)}]
                 \node at (0,1) [font=\small\sffamily] {A} ;
	\end{scope}
     \end{tikzpicture}
     };
     \node [right=of A] (B) {
     \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (d) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_FDR_5000.pdf}};
        \begin{scope} [x={(d.south east)},y={(d.north west)}]
            \node at (0,1) [font=\small\sffamily] {B} ;
\end{scope}
    \end{tikzpicture}
    };
  \node [below=of A] (C) {
\begin{tikzpicture}
    \node[anchor=south west,inner sep=0] at (0,0) (e) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_ROC_1000.pdf}};
    \begin{scope} [x={(e.south east)},y={(e.north west)}]
        \node at (0,1) [font=\small\sffamily] {C} ;
    \end{scope}
    \end{tikzpicture}
    };
    \node [right=of C] (D) {
    \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (f) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_FDR_1000.pdf}};
        \begin{scope} [x={(f.south east)},y={(f.north west)}]
        \node at (0,1) [font=\small\sffamily] {D} ;
        \end{scope}
    \end{tikzpicture}
    };
    \node [below=of C] (E) {
    \begin{tikzpicture}
     \node[anchor=south west,inner sep=0] at (0,0) (g) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_ROC_1000.pdf}};
         \begin{scope} [x={(g.south east)},y={(g.north west)}]
                 \node at (0,1) [font=\small\sffamily] {E} ;
	\end{scope}
     \end{tikzpicture}
     };
     \node [right=of E] (F) {
     \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (h) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_FDR_1000.pdf}};
        \begin{scope} [x={(h.south east)},y={(h.north west)}]
            \node at (0,1) [font=\small\sffamily] {F} ;
\end{scope}
    \end{tikzpicture}
    };
 \end{tikzpicture}
   \caption{Unconstrained MIMOSA model fit to data from a model violating model assumptions and to two-sided data with small counts. Data was simulated from a model where proportions were sampled from a truncated normal distribution over $[0,1]$ rather than a Beta distribution.  A) The average ROC from 10 simulation with N=5,000 events. B) The average observed and nominal FDR from 10 simulations with N=5,000 events. C) Average ROC for N=1,000 events D) Average observed and nominal FDR for N=1,000 events. MIMOSA fit to two-sided data were simulated from the standard model with N=1,000 events. E) Average ROC curves from 10 simulations and F) average observed vs nominal FDR from 10 simulations.}
   \label{webfig:simulations_trunc}
\end{figure}
\bibliographystyle{biom}
\bibliography{MIMOSA}

>>>>

  %  \node at (8,-4) [font=\small\sffamily] {F} ;
%    \node at (0,-7.75) [font=\small\sffamily] {G} ;
  %  \node at (8,-7.75) [font=\small\sffamily] {H} ;
   % \node at (0,-11.75) [font=\small\sffamily] {I} ;
   % \node at (8,-11.75) [font=\small\sffamily] {J} ;
    \end{tikzpicture}
   \caption{Comparison of MIMOSA on other cytokines and cytokine combinations for ENV-1-PTEG stimulated CD4+ T-cells from the HVTN065 trial. This figure appears in color in the electronic version of this article.}
\label{webfig:HVTN065Results}
\end{figure}

@@

\begin{figure} %  figure placement: here, top, bottom, or page
   \centering
\begin{tikzpicture} [auto,node distance=0cm]
%\node at (0,0) (A) {
%\begin{tikzpicture}
%    \node[anchor=south west,inner sep=0] at (0,0) (a) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_ROC_5000.pdf}};
%    \begin{scope} [x={(a.south east)},y={(a.north west)}]
%        \node at (0,1) [font=\small\sffamily] {A} ;
%    \end{scope}
%    \end{tikzpicture}
%    };
%    \node [right=of A] (B) {
%    \begin{tikzpicture}
%    \node[anchor=south west, inner sep=0] at (0,0) (b) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_FDR_5000.pdf}};
%        \begin{scope} [x={(b.south east)},y={(b.north west)}]
%        \node at (0,1) [font=\small\sffamily] {B} ;
%        \end{scope}
%    \end{tikzpicture}
%    };
    \node at (0,0) (A) {
    \begin{tikzpicture}
     \node[anchor=south west,inner sep=0] at (0,0) (c) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_ROC_5000.pdf}};
         \begin{scope} [x={(c.south east)},y={(c.north west)}]
                 \node at (0,1) [font=\small\sffamily] {A} ;
	\end{scope}
     \end{tikzpicture}
     };
     \node [right=of A] (B) {
     \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (d) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_FDR_5000.pdf}};
        \begin{scope} [x={(d.south east)},y={(d.north west)}]
            \node at (0,1) [font=\small\sffamily] {B} ;
\end{scope}
    \end{tikzpicture}
    };
  \node [below=of A] (C) {
\begin{tikzpicture}
    \node[anchor=south west,inner sep=0] at (0,0) (e) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_ROC_1000.pdf}};
    \begin{scope} [x={(e.south east)},y={(e.north west)}]
        \node at (0,1) [font=\small\sffamily] {C} ;
    \end{scope}
    \end{tikzpicture}
    };
    \node [right=of C] (D) {
    \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (f) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_FDR_1000.pdf}};
        \begin{scope} [x={(f.south east)},y={(f.north west)}]
        \node at (0,1) [font=\small\sffamily] {D} ;
        \end{scope}
    \end{tikzpicture}
    };
    \node [below=of C] (E) {
    \begin{tikzpicture}
     \node[anchor=south west,inner sep=0] at (0,0) (g) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_ROC_1000.pdf}};
         \begin{scope} [x={(g.south east)},y={(g.north west)}]
                 \node at (0,1) [font=\small\sffamily] {E} ;
	\end{scope}
     \end{tikzpicture}
     };
     \node [right=of E] (F) {
     \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (h) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_FDR_1000.pdf}};
        \begin{scope} [x={(h.south east)},y={(h.north west)}]
            \node at (0,1) [font=\small\sffamily] {F} ;
\end{scope}
    \end{tikzpicture}
    };
 \end{tikzpicture}
   \caption{Unconstrained MIMOSA model fit to data from a model violating model assumptions and to two-sided data with small counts. Data was simulated from a model where proportions were sampled from a truncated normal distribution over $[0,1]$ rather than a Beta distribution.  A) The average ROC from 10 simulation with N=5,000 events. B) The average observed and nominal FDR from 10 simulations with N=5,000 events. C) Average ROC for N=1,000 events D) Average observed and nominal FDR for N=1,000 events. MIMOSA fit to two-sided data were simulated from the standard model with N=1,000 events. E) Average ROC curves from 10 simulations and F) average observed vs nominal FDR from 10 simulations. This figure appears in color in the electronic version of this article.}
   \label{webfig:simulations_trunc}
\end{figure}
\bibliographystyle{biom}
\bibliography{MIMOSA}
